Questions to Developers

### 2021-06-25 StateOfPractice/Ao-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Update Overall Process slide
Modify Measurements Made slide
Domain analysis and features, change the maintainability, rather than full ranking

\begin{frame}
\frametitle{Summary of Measures}

\bi
\item Empirical measures (number of stars, forks, pull requests, lines of code, etc)
\item Measurement template
\bi
\item Installability
\item Correctness and verifiability
\item Surface reliability
\item Surface robustness
\item Surface usability
\item Maintainability
\item Reusability
\item Surface understandability
\item Visibility/transparency
\ei
\item Developer interviews (looking for pain points)
\item AHP Process with pairwise comparisons
  \ei
\end{frame}

\begin{frame}
\frametitle{Thoughts on Overall Ranking?}

    \includegraphics[width=1.0\textwidth]{overall_scores.png}

@@

\begin{frame}
\frametitle{Ranking Follow-Up}

\bi
\item \structure{We would like feedback on the ranking for each of the qualities}
\item \structure{Is it feasible to review all 10 graphs, and the associated write-up?}
\item \structure{Maybe there is a grad student that can review the rankings?}
\ei

>>>>

\begin{frame}
\frametitle{Domain Analysis and Features}

\bi
\item \structure{Can we work together on doing the following for the
    paper?}
  \bi
\item Domain analysis
\item List of features
\item Matrix of software related to features \ei \ei

@@

\begin{frame}
\frametitle{Measurements Made}

\be
\item Installability
\item Correctness and verifiability
\item Surface reliability
\item Surface robustness
\item Surface usability
\item Maintainability
\item Reusability
\item Surface understandability
\item Visibility and transparency
 \ee

\begin{frame}
\frametitle{Maintainability Measurement}

\includegraphics[width=1.0\textwidth]{maintainability_scores.png}

    \structure{Does anything stand out?}

\begin{frame}
\frametitle{Domain Expert: Ranking Follow-Up}

\bi
\item \structure{Can you review the full ranking measurements?}
\bi
\item There are 9 measurements
\item The write up is about 10 pages long \ei \ei
